### 2020-01-10 report/02-methods.Rmd
Begin manuscript

habitat <- hab_analysis %>%
  mutate_all(list(as.factor)) %>%
  select(-opcod, -station, -aqua_vg)

lvl <- c("null", "weak", "medium", "high")
lvl_sinuosite <- c("straight", "sinuous", "very_sinuous", "meandering")
lvl_shade <- c("clear", "quite_clear", "quite_covered", "covered")

habitat_station <- hab_analysis %>%
  select(-opcod, -aqua_vg, - shade, - sinuosite) %>%
  mutate_if(is.character, list(~factor(., levels = lvl, ordered = TRUE))) %>%
  left_join(select(hab_analysis, station, shade, sinuosite)) %>%
  mutate(
    shade = factor(shade, levels = lvl_shade, ordered = TRUE),
    sinuosite = factor(sinuosite, levels = lvl_sinuosite, ordered = TRUE)) %>%
  group_by(station) %>%
  summarise_all(list(med = ~median(as.numeric(.), na.rm = TRUE))) %>%
  left_join(select(temporal_station_desc, station, width_river_mean, avg_depth_station_mean, width_river_cv, avg_depth_station_cv))

# Add alt, lat, etc...
habitat_station %<>% 
  left_join(geo_station, by = "station") %>%
  select(-region_csp)

# Add temp and flow
flow_temp <- temporal_press_polluants %>%
  filter(category %in% c("flow", "temperature", "DBO", "herbicides",
      "fungicides", "insecticides", "nitrates", "phosphore")) %>%
  rename(station = id) 
flow_temp_med <- flow_temp %>%
  mutate(category = str_c(category, "_med")) %>%
  select(station, category, press_med) %>%
  spread(category, press_med)
flow_temp_cv <- flow_temp %>%
  mutate(category = str_c(category, "_cv")) %>%
  select(station, category, cv_press) %>%
  spread(category, cv_press)

habitat_station %<>%
  left_join(left_join(flow_temp_med, flow_temp_cv, by = "station"), by = "station") %>%
  filter(station %in% op_analysis$station)
habitat_pressure <- habitat_station
```

@@

```{r pca_rotated_plot}
plot_grid(plotlist=test)
```

>>>>

habitat_pressure <- build_habitat_pressure_dataset(
  .habitat_analysis = hab_analysis,
  .tmp_press = temporal_press_polluants,
  .tmp_st_desc = temporal_station_desc,
  .geo_st = geo_station 
)
```

@@

```{r pca_rotated_plot}
plot_grid(plotlist = test)
```
